An Algorithm for In-Situ Bus Scheduling and Passenger State Update

### 2019-04-22 Report/paper.tex
Update paper.tex

\section{Conclusion}

>>>>

\section{Conclusion}
In this project, we propose the smart bus system to offer a flexible usage for dynamically calculating the route to serve passengers and efficiently shorten the regular route to save more waiting time of passengers as well as travel time of buses. A low power Bus Service Access Points (BSAPs) with Wi-Fi and LPWAN interfaces operates as the mobile or static node to form a mobile ad-hoc network to provide high speed transmission in short distance and low speed transmission in long distance for connectivity. Due to its property of low power and portability, this network can be easily deployed to satisfy different topologies and provide pickup/delivery service even though within the area out of Internet coverage. All BSAPs composing a closed network can serve passengers over different locations in a distributed way. Thus, compared to traditional approach with centralized processing, the proposed distributed algorithm makes the network message complexity reduced and time complexity comparable.

Adapting to the real time passenger requests, the dynamic route scheduling problem in the smart bus system is to minimize the total travel time, sum of lateness over all pick-up and delivery locations, and sum of overtime over all buses. This distributed algorithm focuses on solving the problem by introducing the concept of route flexibility of each bus. Therefore, maximizing the total route flexibility also achieve the optimization of the problem. Moreover, the route assignment scheme is proposed to consider the urgency of requests to effectively achieve the flexibility optimization.

Our implementation aims to demonstrate the generation of request as passengers at different locations launch request at different time, the process of assigning requests from bus stops to the matched buses, and the route information updating for buses to sharing the current route and served passenger information to necessary bus stop. The Samraksh Emulator is feasible to implement the relevant features and easy to show all passenger, bus, and bus stop activities within a short time. The implementation is composed by three different kinds of nodes, request driver, bus driver, and bus stop driver, which simulate how passenger requests are served and how bus routes are optimized by maximizing the route flexibility in a smart bus system.

The simulation results show that the bus scheduling algorithm acts with less bus travel time and less lateness over service locations compared to the scenario of the traditional fixed route buses. Also, the simulated system can resolve the problem of inconsistency. (For example, a request is served by more than one buses.) Last but not the least, we encounter some message errors when increasing the number of bus stops. The system might stop since one of the bus stops received an unexpected message from network. Otherwise, the functionalities of request driver, bus driver, and bus stop driver work well with different scenario combinations.
